FinalManuscript_DISCS_UG

### 2018-10-07 parts/02_relatedliterature_07previousimplementations.tex
Forgot to uncomment a paragraph

%This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosytems have yet to be implemented for image processing operations.

>>>>

This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosytems have yet to be implemented for image processing operations.
